Automated Metadata Generation for Fish Specimen Image Collections {\footnotesize \thanks{NSF Grant ???} }

### 2021-03-31 paper/paper_new.tex
Added images
Updates from Overleaf
Merged most of Sect. 6 into Sect. 5.

@@

@@

@@

\subsection{Brightness/Uniformity Results?}
\begin{figure}[H]
  \centering
  \includegraphics[width=\linewidth]{images/histo}
  \caption{Histogram for brightness.}
\end{figure}
\textbf{Todo}: It looks like we should leave out Uniformity.

@@

@@

\section{Discussion}
\textbf{Todo}: Will need some sort of intro/framing paragraph
%DRAFT from jg: Our results provide insight into how off-the-shelf software, supplemented by additional XXX [programming?] can support automatic metadata generation. Results are promising in a number of respects, helping us to identify more clearly areas, where more work is needed [e.g., failed fish, failed rulers]
%Discussion needed to weave in at least a couple of citations. Happy to discuss
\begin{figure}[H]
  \centering
  \includegraphics[width=0.49\linewidth]{images/none1}
  \includegraphics[width=0.49\linewidth]{images/double1}
  \caption{An example of a fish that was not detected (left) and a fish that was detected twice (right).}
\end{figure}
\subsection{Results}\todo{Just going to put the results discussion in small sections and we can change it later if that doesn't make sense}
\subsubsection{Object Detection}

\begin{itemize}
    \item Worked fairly well all things considered
    \item Talk about which fish failed
    \item Talk about which rulers failed
\end{itemize}
\begin{figure}[H]
  \centering
  \includegraphics[width=0.49\linewidth]{images/wrong_side_orig}
  \includegraphics[width=0.49\linewidth]{images/wrong_side1}
  \caption{A fish for which a splotch on its tail fin was labeled the most likely eye.}
\end{figure}
\subsubsection{Side Detection}
There were six cases where an eye was detected but the \verb|side| value
was wrong. Here, a spot on the wrong side of the fish was labeled as the
most likely eye within the bounding box of the fish, i.e.~eye detection 
was incorrect.
There were an additional 17 images for which the automated process generated a result that did not match the manually created data. For these remaining cases the manual data was incorrect, giving the automated system an error rate \(2.8\) times lower than the human error rate.
This result highlights the additional utility of automated methods to
double-check and verify human-generated metadata.

\subsubsection{Clock Value}
\begin{figure}[H]
  \centering
  \includegraphics[width=0.49\linewidth]{images/curved1}
  \caption{An example of a heavily curved specimen.}
  \label{fig:curvedFish}
\end{figure}
Of the specimens for which clock values were generated, 33 did not match the manually created data (within a tolerance of \(\pm{}1\)).
For 25 of those, the human-generated data was incorrect, giving the automated process a \(3.1\) times lower error rate. Of the remaining 8, 2 specimens were quite curved making it difficult to assign a clear angle value, as
seen in Figure \ref{fig:curvedFish}.
The other 6 were values of 3 instead of 9 or vice versa, which resulted from
a mislabeled eye as discussed in the previous section.
\todo{Why is the following sentence here? What does it have to do with
Clock Value?}
A small number of images (such as on the right in Figure~\ref{fig:teaser}) have tags that overlap with the fish. These tags were light enough that they were correctly labeled as background by the pixel analysis.

\subsubsection{Mask and Bounding Box}
\begin{figure}[H]
  \centering
  \includegraphics[width=0.49\linewidth]{images/61631}
  \includegraphics[width=0.49\linewidth]{images/61631_mask}
  \caption{An example of a light colored tail being missed during the pixel analysis process.}
\end{figure}
Masks and bounding boxes contain the head and trunk of the fish in nearly all cases, but there is still more fine tuning to be done to ensure that light fins and tails are masked consistently and accurately.\todo{Talk about ideas for fixing here, or in future work? Or both?}

@@

\subsubsection{Scale and Length}
\begin{figure}[H]
  \centering
  \includegraphics[width=0.49\linewidth]{images/54172}
  \includegraphics[width=0.49\linewidth]{images/54172_mask}
  \caption{An example of a light colored tail being missed during the pixel analysis process.}
  \label{fig:scale_len}
\end{figure}
Scale calculations using the ``2'' and ``3'' method are nearly identical to those calculated by hand between the tick marks on the ruler. When the tail of the fish is accurately masked and the specimen is fairly straight, the length calculation is highly accurate as well. An example of such a result can be seen in Figure~\ref{fig:scale_len}, for which the difference between the hand measured length and the automatically calculated length was only \(0.6\%\) (\(8.88\) cm vs \(8.82\) cm). Thus, the primary means of lowering the error of the length calculation is to improve tail masking accuracy.

>>>>

\begin{itemize}
    \item Worked fairly well all things considered
    \item Talk about which fish failed
    \item Talk about which rulers failed
\end{itemize}
\begin{figure}[H]
  \centering
  \includegraphics[width=0.49\linewidth]{images/wrong_side_orig}
  \includegraphics[width=0.49\linewidth]{images/wrong_side1}
  \caption{A fish for which a splotch on its tail fin was labeled the most likely eye.}
\end{figure}

@@

There were six cases where an eye was detected but the \verb|side| value
was wrong. Here, a spot on the wrong side of the fish was labeled as the
most likely eye within the bounding box of the fish, i.e.~eye detection 
was incorrect.
There were an additional 17 images for which the automated process generated a result that did not match the manually created data. For these remaining cases the manual data was incorrect, giving the automated system an error rate \(2.8\) times lower than the human error rate.
This result highlights the additional utility of automated methods to
double-check and verify human-generated metadata.

\begin{figure}[H]
  \centering
  \includegraphics[width=0.49\linewidth]{images/none1}
  \includegraphics[width=0.49\linewidth]{images/double1}
  \caption{An example of a fish that was not detected (left) and a fish that was detected twice (right).}
\end{figure}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.49\linewidth]{images/curved1}
  \caption{An example of a heavily curved specimen.}
  \label{fig:curvedFish}
\end{figure}
Of the specimens for which clock values were generated, 33 did not match the manually created data (within a tolerance of \(\pm{}1\)).
For 25 of those, the human-generated data was incorrect, giving the automated process a \(3.1\) times lower error rate. Of the remaining 8, 2 specimens were quite curved making it difficult to assign a clear angle value, as
seen in Figure \ref{fig:curvedFish}.
The other 6 were values of 3 instead of 9 or vice versa, which resulted from
a mislabeled eye as discussed in the previous section.
\todo{Why is the following sentence here? What does it have to do with
Clock Value?}
A small number of images (such as on the right in Figure~\ref{fig:teaser}) have tags that overlap with the fish. These tags were light enough that they were correctly labeled as background by the pixel analysis.

@@

\subsection{Brightness/Uniformity Results?}
\begin{figure}[H]
  \centering
  \includegraphics[width=0.49\linewidth]{images/dark}
  \includegraphics[width=0.49\linewidth]{images/normal}
  \includegraphics[width=0.49\linewidth]{images/bright}
  \caption{Examples of low, normal and high contrast fish images.}
\end{figure}
\begin{figure}[H]
  \centering
  \includegraphics[width=\linewidth]{images/histo}
  \caption{Histogram for difference in brightness between foreground an background.}
\end{figure}
\textbf{Todo}: It looks like we should leave out Uniformity.

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.49\linewidth]{images/61631}
  \includegraphics[width=0.49\linewidth]{images/61631_mask}
  \caption{A fish for which the masking and measurement process was highly accurate.}
\end{figure}
Masks and bounding boxes contain the head and trunk of the fish in nearly all cases, but there is still more fine tuning to be done to ensure that light fins and tails are masked consistently and accurately.\todo{Talk about ideas for fixing here, or in future work? Or both?}

@@

\begin{figure}[H]
  \centering
  \includegraphics[width=0.49\linewidth]{images/54172}
  \includegraphics[width=0.49\linewidth]{images/54172_mask}
  \caption{An example of a light colored tail being missed during the pixel analysis process.}
  \label{fig:scale_len}
\end{figure}
Scale calculations using the ``2'' and ``3'' method are nearly identical to those calculated by hand between the tick marks on the ruler. When the tail of the fish is accurately masked and the specimen is fairly straight, the length calculation is highly accurate as well. An example of such a result can be seen in Figure~\ref{fig:scale_len}, for which the difference between the hand measured length and the automatically calculated length was only \(0.6\%\) (\(8.88\) cm vs \(8.82\) cm). Thus, the primary means of lowering the error of the length calculation is to improve tail masking accuracy.

\section{Discussion}
\textbf{Todo}: Will need some sort of intro/framing paragraph
%DRAFT from jg: Our results provide insight into how off-the-shelf software, supplemented by additional XXX [programming?] can support automatic metadata generation. Results are promising in a number of respects, helping us to identify more clearly areas, where more work is needed [e.g., failed fish, failed rulers]
%Discussion needed to weave in at least a couple of citations. Happy to discuss

\subsection{Results}\todo{Just going to put the results discussion in small sections and we can change it later if that doesn't make sense}

@@
